logbook simulations

### 2020-03-23 simulation/README.Rmd
Update simulations log

Checkout results first hyperopt: 
LCTW - no output?? 
RCTW - only 'current'
```{r}
todo <- huh(todo, c("LCTW", "RCTW"), "one", "ace")
```

NCDW - loss still going down, sent in for another 12 hours. 
```{bash, eval = FALSE}
./cart_hyper_run.py hyper-active -t 12:00:00 -m nn-2-layer -b double -e doc2vec -q max -d ace -r 23 # 7811926
```

>>>>

### Checkout results first hyperopt 
LCTW - no output? 
RCTW - only 'current'
```{r}
todo <- huh(todo, c("LCTW", "RCTW"), "one", "ace")
```

```{bash, eval = FALSE}
# LCTW 
# made a mistake in command, "logistic" instead of "lr", run again 
./cart_hyper_run.py hyper-active -t 03:00:00 -m logistic -b double -e tfidf -q max -d ace -r 23 # 7813556

# RCTW, fixed a parameter bug in simulation package. 
./cart_hyper_run.py hyper-active -t 03:00:00 -m rf -b double -e tfidf -q max -d ace -r 23 # 7813592
```

```{r}
todo <- busy(todo, c("LCTW", "RCTW"), "one", "ace")
```

NCDW - loss still going down, sent in for another 12 hours. 
```{bash, eval = FALSE}
# NCDW
./cart_hyper_run.py hyper-active -t 12:00:00 -m nn-2-layer -b double -e doc2vec -q max -d ace -r 23 # 7811926
```
